Cloud-SAP: Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments

### 2013-09-16 article/article.tex
Add some bibligraphy to the article

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\usepackage[utf8]{inputenc}
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{array}
\newcolumntype{C}{>{\centering\arraybackslash}p{3.4cm}}
\newcolumntype{L}{>{\arraybackslash}p{2.5cm}}

@@

\section{Introduction}
\label{intro}
Cloud computing, a relatively new concept which denotes offering computing utilities on demand in a pay-as-you-go manner like any other services available in today's society, has already started the process of transforming IT industry, making an impact on the way the software/hardware is produced and perceived. Because of its widespread presence in the IT community, this model makes computing resources more and more attractive for broader audience, especially in diverse branches of business, e.g. pharmaceutical or construction.

There are a few noticeable things which can be considered innovative in the way the services are provided. Firstly, clients of such services have no knowledge of the physical location of resources they use. Secondly, they are under illusions of infinite resources that are available. What is more, they pay providers only when they really use their services -- this means they do not need to invest heavily in building and maintaining hardware infrastructure. Last but not least, in order to ease dynamic resource management and manipulation, cloud providers use various virtualization technologies which operate on different levels, e.g. server, network or storage.

\subsection{Service Models}
Cloud computing classified the delivered services to three categories: Infrastructure as a Service (IaaS), Platform as a Service (PaaS) and Software as a Service (SaaS). They provide the consumer with infrastructure, deployment platform (application ecosystem) and software respectively. The just defined terms are commonly referred to in the Cloud community as \emph{service models}.

@@

Such a model has been devised and named \emph{InterCloud}. In this solution resources are managed in a market-oriented fashion that enables dynamic regulation of the supply and demand of resources and promotes the mechanisms for their allocation that would take into account their priorities and levels of utilization.

\subsection{Application scaling}
Scalability is a widely accepted measure for improving application performance, consequently increasing offered Quality-of-Service. Despite the lack of a clear definition, in this article we consider this term an ability to work without delays and unproductive resource consumption at light, moderate, or heavy loads while making good use of available resources (in some works it is referred to as \emph{load scalability}).

@@

\section{Who is Who in cloud provisioning}
In the context of this article, the main point of interest are providers which offer features related to resource management, monitoring and utilization. In general, current key providers include Amazon \emph{Web Services}, \emph{Microsoft Azure}, Google \emph{AppEngine} and \emph{Heroku}. Despite not all of them operate on the same level of abstraction, it is possible to compare them as they expose functionalities which can be classified as PaaS. For example, on top of its infrastructure services, Amazon has such products as \emph{Elastic Load Balancer}, \emph{Cloud Watch} and \emph{Auto Scaling} which, to some extent, matches our needs.

@@

\section{Section title}
\label{sec:1}
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

>>>>

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\usepackage[utf8]{inputenc}
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{array}
\newcolumntype{C}{>{\centering\arraybackslash}p{3.4cm}}
\newcolumntype{L}{>{\arraybackslash}p{2.5cm}}

@@

\section{Introduction}
\label{intro}
Cloud computing, a relatively new concept which denotes offering computing utilities on demand in a pay-as-you-go manner like any other services available in today's society, has already started the process of transforming IT industry, making an impact on the way the software/hardware is produced and perceived. Because of its widespread presence in the IT community, this model makes computing resources more and more attractive for broader audience, especially in diverse branches of business, e.g. pharmaceutical or construction \cite{PharmaComputation}.

There are a few noticeable things which can be considered innovative in the way the services are provided. Firstly, clients of such services have no knowledge of the physical location of resources they use. Secondly, they are under illusions of infinite resources that are available \cite{ScalingInDaCloud}. What is more, they pay providers only when they really use their services -- this means they do not need to invest heavily in building and maintaining hardware infrastructure. Last but not least, in order to ease dynamic resource management and manipulation, cloud providers use various virtualization technologies which operate on different levels, e.g. server, network or storage.

\subsection{Service Models}
Cloud computing classified the delivered services to three categories: Infrastructure as a Service (IaaS), Platform as a Service (PaaS) and Software as a Service (SaaS). They provide the consumer with infrastructure, deployment platform (application ecosystem) and software respectively. The just defined terms are commonly referred to in the Cloud community as \emph{service models} \cite{NIST}.

@@

Such a model has been devised and named \emph{InterCloud} \cite{InterCloud}. In this solution resources are managed in a market-oriented \cite{MarketOriented} fashion that enables dynamic regulation of the supply and demand of resources and promotes the mechanisms for their allocation that would take into account their priorities and levels of utilization.

\subsection{Application scaling}
Scalability is a widely accepted measure for improving application performance, consequently increasing offered Quality-of-Service. Despite the lack of a clear definition, in this article we consider this term an ability to work without delays and unproductive resource consumption at light, moderate, or heavy loads while making good use of available resources \cite{ScalabilityTerm} (in some works it is referred to as \emph{load scalability}).

@@

\section{Who is Who in cloud provisioning}
In the context of this article, the main point of interest are providers which offer features related to resource management, monitoring and utilization. In general, current key providers include Amazon \emph{Web Services} \cite{AWS}, \emph{Microsoft Azure} \cite{Azure}, Google \emph{AppEngine} \cite{GoogleAppEngine} and \emph{Heroku} \cite{Heroku}. Despite not all of them operate on the same level of abstraction, it is possible to compare them as they expose functionalities which can be classified as PaaS. For example, on top of its infrastructure services, Amazon has such products as \emph{Elastic Load Balancer}, \emph{Cloud Watch} and \emph{Auto Scaling} which, to some extent, matches our needs.

@@

%\section{Section title}
%\label{sec:1}
%Text with citations \cite{RefB} and \cite{RefJ}.
%\subsection{Subsection title}
%\label{sec:2}
%as required. Don't forget to give each section
%and subsection a unique label (see Sect.~\ref{sec:1}).

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{NIST}
  {Mell, P. and Grance, T.}, {The NIST Definition of Cloud Computing}, 2011
\bibitem{InterCloud}
  {Buyya, R. Ranjan, R. and Calheiros, R.}, {InterCloud: Scaling of Applications across multiple Cloud Computing Environments}, 2010
\bibitem{MarketOriented}
  {Buyyaa, R., Yeoa, C., Venugopala, S., d Broberga, J. and Brandicc, I.}, {Cloud computing and emerging IT platforms: Vision, hype, and reality for delivering computing as the 5th utility}, {Future Generation Computer Systems}, vol.25, 2009
\bibitem{ScalingInDaCloud}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.}, {Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{ScalabilityTerm}
  Bondi, A., {Characteristics of Scalability and Their Impact on Performance}, 2000
\bibitem{PharmaComputation}
  Jon Brodkin, \emph{\$1,279-per-hour, 30,000-core cluster built on Amazon EC2 cloud}, {\emph{Ars Technica}, \url{http://arstechnica.com/business/2011/09/30000-core-cluster-built-on-amazon-ec2-cloud/}}, last access: 16/09/2013
\bibitem{AWS}
  {Amazon Elastic Compute Cloud (EC2)}, {\url{http://aws.amazon.com/}}, last access: 16/09/2013 
\bibitem{GoogleAppEngine}
  {Google App Engine}, {\url{https://appengine.google.com/}}, last access: 16/09/2013 
\bibitem{Heroku}
  {Heroku}, {\url{https://www.heroku.com}}, last access: 16/09/2013 
\bibitem{Azure}
  {Windows Azure}, {\url{www.windowsazure.com/}}, last access: 16/09/2013 
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}
